The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-02-11 paper/ms.tex
I am hungry

\begin{figure}
  \includegraphics[scale=0.35]{f6.eps}
  \caption{Escape fraction as a function of rotational velocity. All
    these models have $\tau_{a}=1$. The continuous (dashed) lines
    correspond to central (homogeneous) models.
    \label{fig:efvsv}}
\end{figure}

\begin{figure}
  \includegraphics[scale=0.35]{f7.eps}
  \caption{Escape fraction as a function of the
    product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
    the infinite slab is shown as a continuous line. Different dashed
    lines correspond to different rotational velocities.
    {\bf IS THE ALBEDO TAKEN INTO ACCOUNT?}
    \label{fig:efvsNeufeld}}   
\end{figure}

@@

\subsection{Anisotropy and off-centered emission}

\label{sec:off-center}
\begin{figure}
\begin{center}
  \includegraphics[scale=0.35]{f8.eps}
  \caption{The two small circles show the two different spherical
    off-centered emitting regions with respect to the larger spherical
    gas distribution. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (outwards the
    page). In order to study a possible anysotropy we place an
    observer along the the $\hat{\j}$ direction. The vector
    $\hat{k}_{\rm out}$ represents the outgoing direction of an
    escaping \ly photon. 
    \label{fig:OCspheres}}

\end{center}
\end{figure}

\begin{figure}
  \includegraphics[scale=0.35]{f9.eps}
  \caption{$\mu$ histogram showing the orientation effects for the different
  distributions central(Points line), homogeneous(Dashed) and off-Center(Solid line).  
    \label{fig:muhisto}} 
\end{figure}

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[scale=0.35]{f6.eps}
  \includegraphics[scale=0.35]{f7.eps}
\end{center}
  \caption{Effects of rotaation on the escape fraction. Left
    panel. Escape fraction as a function of rotational velocity. All
    these models have $\tau_{a}=1$. The continuous (dashed) lines
    correspond to central (homogeneous) models. Right panel. Escape
    fraction as a    function of the product $(a\tau_{\rm
      H})^{1/3}\tau_{a}$. The    analytic solution for the infinite
    slab is shown as a continuous    line. Different lines correspond
    to different rotational    velocities.     \label{fig:efvsv}} 
\end{figure*}

%\begin{figure}
%  \caption{

%    {\bf IS THE ALBEDO TAKEN INTO ACCOUNT?}
%    \label{fig:efvsNeufeld}}   
%\end{figure}

@@

\subsection{Anisotropy and off-centered emission}
\label{sec:off-center}

\begin{figure}
\begin{center}
  \includegraphics[scale=0.35]{f8.eps}
\end{center}
\caption{Schematic representation of the geometry for the off-center
  emission. The large circle represents the gas distribution and the
    two smaller circles the off-centered \ly emitting regions. The angular
    velocity vector lies along $\hat{k}$ direction
    towards the reader. The vector $\hat{k}_{\rm out}$ represents the
    outgoing direction of an escaping \ly photon and the observer is
    placed along the $\hat{j}$ direction. The distribution of $\Theta$
    angles is used to study potential emission anisotropies. 
    \label{fig:OCspheres}}
\end{figure}

\begin{figure}
  \includegraphics[scale=0.35]{f9.eps}
  \caption{Histogram of $\mu\equiv\cos\Theta$ for the 
    central (dotted), homogeneous (dashed) and off-center (solid
    line) distributions. Deviations from a flat distribution signal the presence of
    spatial emission anisotropies. 
    \label{fig:muhisto}} 
\end{figure}
